Home Nighttime Cough Monitoring

### 2024-12-07 Lilah Melzer/cough_monitor_analysis.qmd
file paths

start_end <- read.csv("C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF/Lilah Melzer/Home Nighttime Cough Monitoring/Data_Clean/Start and end dates.csv",

@@

vacations <- read.csv("C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF/Lilah Melzer/Home Nighttime Cough Monitoring/Data_Clean/Vacation days.csv",

@@

  "C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF/Lilah Melzer/Home Nighttime Cough Monitoring/Data_Raw/Cough_w_TotalCounts_0824 - Cough_agg_w_count_0828.csv",

@@

write.csv(agg_counts, file = "C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF/Lilah Melzer/Home Nighttime Cough Monitoring/Data_Clean/cleaned_aggregated_counts.csv", na = "", row.names = F)

>>>>

start_end <- read.csv("/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor/Data_Clean/Start and end dates.csv",

@@

vacations <- read.csv("/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor/Data_Clean/Vacation days.csv",

@@

  "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor/Data_Raw/Cough_w_TotalCounts_0824 - Cough_agg_w_count_0828.csv",

@@

write.csv(agg_counts, file = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor/Data_Clean/cleaned_aggregated_counts.csv", na = "", row.names = F)
